Approximation as Differentiation

### 2025-04-23 main/introduction.tex
[ paper ] explain the forward slicing too

>>>>

  In this case, the forwards portion of the Galois connection tells us for each approximation of the input whether or not it is sufficient to compute the output. In this example, if we provide insufficient data to compute the output, then we will get an underapproximated output. For example, $\partial (\mathit{query}\, \mathsf{a})_f([(\mathsf{a},0),(\mathsf{b},\bot),(\mathsf{a},\bot)]) = \bot$ because we need all the values associated with the label $\mathsf{a}$ to compute their sum.
